\documentclass[12pt, a4paper]{report}  % or report/book/ieeeconf
\usepackage[utf8]{inputenc}             % Encoding
\usepackage[T1]{fontenc}                % Better font handling
\usepackage[english]{babel}            % Language settings
\usepackage{graphicx}                   % For images
\usepackage{hyperref}                   % Clickable links
\usepackage[backend=biber,style=apa]{biblatex}
\usepackage{enumitem}

\addbibresource{references.bib} 

% ===== Document Structure =====
\begin{document}

% Title
\title{Workshop No. 1 — Kaggle Systems Engineering Analysis}
\author{Juan David Escallon Guzmán \and Juan Diego Lozano Luna \and Jorge Eduardo Muñoz Gomez}
\maketitle

% Table of Contents
\tableofcontents
\newpage

% Summary of the competition
\input{escallon/MainObjective.tex} 

% Key Elements
\input{jorge/keyElements.tex} 

%System Mapping
\input{lozano/relationshipsMapping.tex}

%Sensitivity
\input{jorge/sensitivity.tex} 

%Chaos Theory
\input{escallon/Chaos.tex}

%Conclusion
\input{lozano/conclusions.tex}
\begin{thebibliography}{9}

    \bibitem{kaggle_football}
    Google. \emph{Google Research Football with Kaggle}, 2020.\\
    \url{https://www.kaggle.com/competitions/google-football/overview}.\\
    Accessed: 2025-04-04.
    
    \bibitem{rules_of_football}
    Rules of Sport. \emph{Football Rules}.\\
    \url{https://www.rulesofsport.com/sports/football.html}.\\
    Accessed: 2025-04-04.
    
    \bibitem{kaggle_football_json}
    Kaggle. \emph{Football Environment JSON Config}.\\
    \url{https://github.com/Kaggle/kaggle-environments/blob/master/kaggle_environments/envs/football/football.json}.\\
    Accessed: 2025-04-04.
    
    \bibitem{kaggle_football_py}
    Kaggle. \emph{Football Environment Python File}.\\
    \url{https://github.com/Kaggle/kaggle-environments/blob/master/kaggle_environments/envs/football/football.py}.\\
    Accessed: 2025-04-04.
    
    \bibitem{google_research_football}
    Google Research. \emph{Google Research Football GitHub Repository}.\\
    \url{https://github.com/google-research/football/}.\\
    Accessed: 2025-04-04.
    
    \bibitem{google_research_observation}
    Google Research. \emph{Google Football Observation Documentation}.\\
    \url{https://github.com/google-research/football/blob/master/gfootball/doc/observation.md#raw-observations}.\\
    Accessed: 2025-04-04.
    
    \end{thebibliography}
    
\end{document}